Introducing the \NAME Framework\\ for Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-15 paper.tex
added draft figures

\usepackage{tikz}

@@

\begin{figure}[H]
\begin{tikzpicture}[
    nonterminal/.style={
% The shape:
rectangle,
% The size:
      minimum size=6mm,
% The border:
      very thick,
      draw=red!50!black!50,
      % The filling:
top color=white,
bottom color=red!50!black!20, % and something else at the bottom % Font
font=\itshape
    }]
  \node [nonterminal] {TODO};
\end{tikzpicture}
\caption{Overview code generation process}
\label{fig:code-generation}
\end{figure}

@@

\begin{figure}[H]
\begin{tikzpicture}[
    nonterminal/.style={
% The shape:
rectangle,
% The size:
      minimum size=6mm,
% The border:
      very thick,
      draw=red!50!black!50,
      % The filling:
top color=white,
bottom color=red!50!black!20, % and something else at the bottom % Font
font=\itshape
    }]
  \node [nonterminal] {TODO};
\end{tikzpicture}
\caption{Semantic Model Meta-Model}
\label{fig:meta-model}
\end{figure}

>>>>

\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usetikzlibrary{graphs}
\usetikzlibrary{trees}

@@

\tikzset{
  resource/.style={
    rectangle,
    minimum size=7mm,
    thick, draw=black,
    top color=white,
    font=\ttfamily
  },
  representation/.style={
    rectangle, minimum size=6mm, rounded corners=3mm,
    minimum size=7mm,
    thick, draw=black,
    top color=white,
    font=\itshape
  }
}

\begin{figure}[H]
\begin{tikzpicture}[
  node distance=8mm,
  ,>=stealth,thick,black!50,text=black,
  every new ->/.style={shorten >=1pt},
]
  \node (dsl)  [resource]                    {DSL};
  \node (sm)   [representation,right=of dsl] {Semantic\\Model};
  \node (cm)   [representation,right=of sm]  {Code\\Model};
  \node (code) [resource,right=of cm]        {Code};

  \draw [->] (dsl) -> (sm)  node [midway,above=10pt] {parse};
  \draw [->] (sm)  -> (cm)   node [midway,above=10pt,align=center] {semantic\\transform};
  \draw [->] (cm)  -> (code) node [midway,above=10pt] {emit code};

  \draw [rounded corners,->]
        ($ (sm.east) - (5mm,3.5mm) $)
        -- ++(0,-.5)
        -| ($ (sm.west) + (5mm,-3.5mm) $)
           node [near start, below=1pt] {type inference};

  \draw [rounded corners,->]
        ($ (cm.east) - (5mm,3.5mm) $)
        -- ++(0,-.5)
        -| ($ (cm.west) + (5mm,-3.5mm) $)
           node [near start, below=1pt,align=center] {syntactic\\transform};

\end{tikzpicture}
\caption{Overview code generation process}
\label{fig:code-generation}
\end{figure}

@@

\tikzset{
  class/.style={
    rectangle,
    minimum size=1cm,
    thick, draw=black,
    text centered,
    text width=1.75cm,
  }
}

\begin{figure}[H]
\begin{tikzpicture}[
  edge from parent fork down,
  sibling distance=5mm, level distance=20mm, node distance=8mm
  ]
  \node (model) [class] {Model}
      child {node (module ) [class] {Module}
        child {node (strategy) [class,align=center,xshift=-9mm] {Execution\\Strategy}
          child {node(every) [class,xshift=-9mm] {Every}}
          child {node (when) [class,xshift=9mm] {When}}
        }
        child {node [class,xshift=9mm] {function}}
      };
  \node (constant) [class,right=of model] {Constant};
  \node (scope)    [class,left=of strategy] {Scope};
\end{tikzpicture}
\caption{Partial Semantic Model Meta-Model}
\label{fig:meta-model}
\end{figure}
